Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-20 paper/paper.tex
fix missing reference
reminder

%\Mar{@Lucas, please look for constant
  %numbers as this *in text* and use macros instead. We do not want to
  %leave inconsistent data in the paper!}
We evaluated \tname\ against \totalAttacks attacks of various kinds, such as 
\Luc{This is already on section V, should it also be here?} Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}. %\Fix{...}\rui{add few examples}. 
The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top five rules in 
\percTopFiveRanking\ of the cases and ranked the correct rule among 
the top ten rules in \topTenAttacks of the \totalAttacks cases. \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

@@

\subsubsection{Comparison with other tools}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
 evolutionaries approaches to 
autonomously generate rules using the Snort IDS. They built 
their own ICMP datasets by using packet creation tools or by capturing network traffic. 
Guruprasad also used DARPA 1999 and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks.

>>>>

%\Mar{@Lucas, please look for constant
  %numbers as this *in text* and use macros instead. We do not want to
  %leave inconsistent data in the paper!}
We evaluated \tname\ against \totalAttacks attacks of various kinds, such as 
\Luc{This is already on section V, should it also be here?} Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}. %\Fix{...}\rui{add few examples}. 
The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top five rules in \Fix{fix values}
\percTopFiveRanking\ of the cases and ranked the correct rule among 
the top ten rules in \topTenAttacks of the \totalAttacks cases. \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

@@

\subsubsection{Comparison with other tools}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
 evolutionaries approaches to 
autonomously generate rules using the Snort IDS. They built 
their own ICMP datasets by using packet creation tools or by capturing network traffic. 
Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
for non-ICMP attacks.
